Excuse me, do you have a moment to talk about version control?

### 2017-07-08 README.Rmd
Blinded and unblinded versions

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- name: Jennifer Bryan
  affiliation: |
    RStudio and the Department of Statistics, University of British Columbia
  thanks: >
    The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton, Colin Rundel, and Hadley Wickham.
blinded: 0
output:
  github_document:
    toc: yes
  rticles::asa_article: null
keywords: |
    data science, workflow, Git, GitHub, R language, R Markdown, reproducibility
abstract: >
    Data analysis, statistical research, and teaching statistics have at least
    one thing in common&#58; these activities all produce many files! There are
    data files, source code, figures, tables, prepared reports, and much
    more. Most of these files evolve over the course of a project and often
    need to be shared with others, for reading or edits, as a project unfolds.
    Without explicit and structured management, project organization can easily
    descend into chaos, taking time away from the primary work and reducing the
    quality of the final product. This unhappy result can be avoided by
    repurposing tools and workflows from the software development world, namely,
    distributed version control. This article describes the use of the version
    control system Git and and the hosting site GitHub for statistical and data
    scientific workflows. Special attention is given to projects that use the
    statistical language R and, optionally, R Markdown documents. Supplementary
    materials include an annotated set of links to step-by-step tutorials,
    real world examples, and other useful learning resources.
bibliography: git-github-for-stats.bib
---

>>>>

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- name: Jennifer Bryan
  affiliation: |
    RStudio and the Department of Statistics, University of British Columbia
  thanks: >
    The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton, Colin Rundel, and Hadley Wickham.
blinded: 0
output:
  rticles::asa_article: null
  github_document:
    toc: yes
keywords: |
    data science, workflow, Git, GitHub, R language, R Markdown, reproducibility
abstract: >
    Data analysis, statistical research, and teaching statistics have at least
    one thing in common&#58; these activities all produce many files! There are
    data files, source code, figures, tables, prepared reports, and much
    more. Most of these files evolve over the course of a project and often
    need to be shared with others, for reading or edits, as a project unfolds.
    Without explicit and structured management, project organization can easily
    descend into chaos, taking time away from the primary work and reducing the
    quality of the final product. This unhappy result can be avoided by
    repurposing tools and workflows from the software development world, namely,
    distributed version control. This article describes the use of the version
    control system Git and and the hosting site GitHub for statistical and data
    scientific workflows. Special attention is given to projects that use the
    statistical language R and, optionally, R Markdown documents. Supplementary
    materials include an annotated set of links to step-by-step tutorials,
    real world examples, and other useful learning resources.
bibliography: git-github-for-stats.bib
---
